Tutorial on Tidymodel

### 2020-04-18 tidymodels/tutorial_in_tidymodels.Rmd
Continuando o tutorial de Tidymodels

rf_fit <- fit(rf_model, price~., dia_juiced)
rf_fit
```

@@

glance(lm_fit$fit)
tidy(lm_fit$fit)
rf_fit$fit

augment(lm_fit$fit) %>% 
  rowid_to_column() %>% 
  select(rowid, price, .fitted:.std.resid)

@@

>>>>

# rf_fit <- fit(rf_model, price~., dia_juiced)
# rf_fit
```

@@

glance(lm_fit$fit)
tidy(lm_fit$fit)
# rf_fit$fit

lm_train_predicted <- augment(lm_fit$fit) %>% 
  rowid_to_column() %>% 
  select(rowid, price, .fitted:.std.resid)
```

ggplot(lm_train_predicted, aes(.fitted, price)) +
  geom_point(alpha=.2)+
  ggrepel::geom_label_repel(aes(label=rowid), data=filter(lm_train_predicted, abs(.resid)>2)) +
  labs(title="Actual vs. Predicted Price of Diamonds")

@@

## Evaluating Model Performance: `yardstick`
